\documentclass{article}
% preamble

# FIXME obiously wrong
\begin{document}
# Maths Nitty Witty Misc Stuff

## Initial setup (load matlib library)
```{r init}
library(matlib)
library(rmarkdown)
library(knitr)
#library(pandoc)  TODO ?? check whether this is correct
knitr::opts_chunk$set(fig.width=9, fig.height=6) # sets up output figs (9 x 6)
```

## 1. INDEXING each matrices variable element
```{r indexing}
A <- matrix(paste0('a_{', outer(1:4, 1:4, FUN  = paste0), '}'), 
            nrow=4)
```

```{r showa}
A
```

# TODO not sure whether this below is correct either

```{r lat}
latexMatrix(
      A
)
```


```{r bxfold}
b <- paste0("b_", 1:4)
x <- paste0("x_", 1:4)
```

```{r bxrun}
b
x
```

TODO renders twice, both times badly, fix

```{r eqn}
latexMatrix(
      matrix(showEqn(A, matrix(b, nrow = 1), vars = matrix(x, nrow = 1)))
)
```

TODO wrong below

$$
\begin{array}{lllllllll}
      a_{11} \cdot x__1 &+& a_{12} \cdot x__2 &+& a_{13} \cdot x__3 &+& a_{14} \cdot x__4  &=&  b_1 \\ 
      a_{21} \cdot x__1 &+& a_{22} \cdot x__2 &+& a_{23} \cdot x__3 &+& a_{24} \cdot x__4  &=&  b_2 \\ 
      a_{31} \cdot x__1 &+& a_{32} \cdot x__2 &+& a_{33} \cdot x__3 &+& a_{34} \cdot x__4  &=&  b_3 \\ 
      a_{41} \cdot x__1 &+& a_{42} \cdot x__2 &+& a_{43} \cdot x__3 &+& a_{44} \cdot x__4  &=&  b_4 \\ 
\end{array}
$$


## 2. DISCOVERED accidentally totally AWESOME COOL FN **`OUTER`**!!!
## TODO learn more about it

## So far I found out:
### The fn takes 1st arg and makes (eg. 1:3) rows as plain chars for each column (thx to FUN paste0),ie.
#### 1, 1, 1, ...
#### 2, 2, 2, ...
#### 3, 3, 3, ...
## But true magic happens when the 2nd argument creates (1:3) columns for each row


# outer(X, Y, FUN = "*", ...) => 1st argument X and 2nd argument Y are usually arrays, vectors
# the easiest way how to understand is like chess: a1, b1, ..., h1 \n a2, b2, ..., h2 \n etc
# fn FUN => it is used as product for each element X times (ie. FUN) each element Y...

### To compile me, use
```{r compile, eval=FALSE}
library(knitr)
knit('math-basic-howtos/some-math-usefulness.Rmd')
```

## 3. ANOTHER quite extraordinary interesting functions - Inverse (or inv) (as well knitr::purl)
## TODO check them and play with them at least for a moment, also, clean this mess:

library(matlib)

A <- matrix( c(5, 1, 0,
               3,-1, 2,
               4, 0,-1), nrow=3, byrow=TRUE)
det(A) # Only non-singular matrices have an inverse.
inv(A)
Inverse(A, verbose=TRUE, fractions=TRUE) #fractions=FALSE) # verbose=TRUE, 


(x <- matrix(1:4, ncol = 2))
unlist(determinant(x))
det(x)

B <- matrix(1:12, 3, 4) / 6
printMatrix(B, fractions=TRUE)
printMatrix(B, latex=TRUE)

library(knitr)
wrap_rmd(text = c("```", "1+1", "```", "- a list item", "> a quote", "",
                  paste(rep("this is a normal paragraph", 5), collapse = " ")))


library(knitr)
(f = system.file("examples", "knitr-minimal.Rmd", package = "knitr"))
knit(f)  # compile to tex

purl(f)  # tangle R code
purl(f, documentation = 0)  # extract R code only
purl(f, documentation = 2)  # also include documentation

unlink(c("knitr-minimal.tex", "knitr-minimal.R", "figure"), recursive = TRUE)

## 4. TODO - another function = echelon(A, b)

\end{document}